Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-27 paper.tex
Add Component - IPFS

\subsubsection{IPFS}

>>>>

\subsubsection{IPFS}
Inter-Planetary File system(IPFS)\cite{IPFS} is a peer-to-peer network for storing and accessing files, websites, applications, and data in a distributed file system which is not maintained with certain nodes or entities but all IPFS users. In our proposed architecture, brokers are responsible to upload the metadata of products, including title, data provider information and data preview to IPFS in order to provide users with search capabilities to meet the consumers' need.
